### 2021-05-13 Paper.tex
modified

\begin{table}[H]
\caption{List of benchmarks implemented for each feature of the code.}
\centering
\begin{tabular}{| l | l |}
\toprule
 \textbf{Feature}  & \textbf{Benchmark}  \\
\midrule
  Solver  & Stokes flow   \\
\hline
  4th-order Runge-Kutta  & \multirow{2}{*}{Zalesak disk} \\
  markers advection  &  \\
\hline
  \multirow{4}{*}{Momentum equation}  & Poiseuille flow   \\
    & Instantaneous 2D sphere   \\
    & Rayleigh-Taylor experiment  \\
    & Falling block  \\
\hline
    & 2D Stokes sphere \\
    Sticky air and  & Stabilisation algorithm   \\
    free surface & Topography relaxation   \\
  & Spontaneous subduction   \\
\hline
  Erosion and sedimentation  & -  \\
\hline
   Non-linear  & Slab detachment   \\
   visco-plasticity & Indenter   \\
    & Brick   \\
\hline
  \multirow{5}{*}{Energy equation}  & Advection stabilisation   \\
    & Simple shear heating \\
    & Shear and adiabatic heating \\
    & Mantle convection   \\
    & Thin layer entrainment   \\
\hline
  Phase changes  & \multirow{2}{*}{Hydrated sinking cylinder} \\
  and hydration  &  \\
\hline
  Melting & Experimental melting curves \\
\bottomrule
\end{tabular}
\label{tab:list}
\end{table}

>>>>

\begin{table}[H]
\caption{List of benchmarks implemented for each feature of the code.}
\centering
\begin{tabular}{| l | l |}
\toprule
 \textbf{Feature}  & \textbf{Benchmark}  \\
\midrule
  Solver  & Stokes flow (Section \ref{sec:stokes})  \\
\hline
  4th-order Runge-Kutta  & \multirow{2}{*}{Zalesak disk (Section \ref{sec:runge})} \\
  markers advection  &  \\
\hline
  \multirow{4}{*}{Momentum equation}  & Poiseuille flow (Section \ref{sec:poiseuille}) \\
    & Instantaneous 2D sphere (Section \ref{sec:ist_sphere})   \\
    & Rayleigh-Taylor experiment (Section \ref{sec:rayleigh})  \\
    & Falling block (Section \ref{sec:block})  \\
\hline
    & 2D Stokes sphere (Section \ref{sec:sphere}) \\
    Sticky air and  & Stabilisation algorithm (Section \ref{sec:stab})   \\
    free surface & Topography relaxation (Section \ref{sec:crameri})   \\
  & Spontaneous subduction (Section \ref{sec:subduction})   \\
\hline
  Erosion and sedimentation  & -  \\
\hline
   Non-linear  & Slab detachment (Section \ref{sec:slab})   \\
   visco-plasticity & Indenter (Section \ref{sec:indenter})   \\
    & Brick (Section \ref{sec:brick})   \\
\hline
  \multirow{5}{*}{Energy equation}  & Advection stabilisation (Section \ref{sec:advection})   \\
    & Simple shear heating (Section \ref{sec:simple_shear}) \\
    & Shear and adiabatic heating (Section \ref{sec:shear}) \\
    & Mantle convection (Section \ref{sec:mantle})   \\
    & Thin layer entrainment (Section \ref{sec:thin})   \\
    & Viscoplastic mantle convection (Section \ref{sec:visco_mantle})   \\
\hline
  Phase changes  & \multirow{2}{*}{Hydrated sinking cylinder (Section \ref{sec:quinquis})} \\
  and hydration  &  \\
\hline
  Melting & Experimental melting curves (Section \ref{sec:katz}) \\
\bottomrule
\end{tabular}
\label{tab:list}
\end{table}
